### 2020-07-21 cases_and_policies/rmd/datasummary.Rmd
new file:   covid.bib 	modified:   datasummary.Rmd

```{r, warning=FALSE}
gv <- dataguide$name[dataguide$source=="Google Mobility Reports"]
hv <- dataguide$name[dataguide$source=="Homebase"]
uv <- c("daily_distance_diff", "daily_visitation_diff",
        "encounters_rate", "log_encounters_rate")
cs$log_encounters_rate <- log(1+cs$encounters_rate)
```

>>>>

```{r, warning=FALSE}
gv <- dataguide$name[dataguide$source=="Google Mobility Reports"]
gv <- gv[grep("_change_from_baseline",gv)]
hv <- dataguide$name[dataguide$source=="Homebase"]
```
